---
title: "Forbes List Analysis"
author: "Josia Schramm, Bernhard Eymann, Nico Joller"
date: "`r Sys.Date()`"
output: html_document
---
## Research Question
We want to analyze the Forbes List of the richest people in the world. We want to find out if there is a correlation between age and net worth and if the distribution of wealth is equal among the continents.
Our hypothesises are 1: There is a correlation between age and net worth. 2: The distribution of wealth is not equal among the continents.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data, libraries
We load the tidyverse library and the data from the data_orig folder.
```{r}
library(tidyverse)
data_orig <- read.csv(here::here("data_orig", "forbes_richman.csv"))

```

## Data cleaning
We clean the data by removing non-integer values from the Net.Worth column and transforming the Age column into a numeric column. We also sort the countries into continents and the industries into fewer categories.

```{r}
You can also embed plots, for example:

```{r pressure, echo=FALSE}

# Frage Bernhard: Was bewirkt dieser Teil?
sapply(data_orig, class)
sapply(data_orig, table)

summary(data_orig)


# remove non integer and non "." in Net.Worth
# Bernhard: Habe ich halb verstanden, aber nicht ganz. Was macht die Funktion genau?
remove_non_integer <- function(vector) {
  vector <- str_replace_all(vector, "[^0-9.]", "")
  vector <- as.numeric(vector)
  return(vector)
}

df <- data_orig

df$Net.Worth <- remove_non_integer(data_orig$Net.Worth)

# mutate chars into factors, mutate age into numeric
#Nico, ifelse versteh ich nicht
df <- df %>% 
  mutate(Age = ifelse(Age == "N/A", NA, Age)) %>% 
  mutate(Age = as.numeric(Age)) %>%
  mutate(Country = ifelse(Country %in% c("Canada", "United States"), "North America", Country)) %>% 
  mutate(Country = ifelse(Country %in% c("Argentina", "Barbados", "Belize", "Brazil", "Chile", "Colombia","Macau", "Guernsey", "Mexico", "Peru", "St. Kitts and Nevis", "Uruguay", "Venezuela"), "South America", Country)) %>% 
  mutate(Country = ifelse(Country %in% c("Austria","Belgium", "Bulgaria", "Cyprus", "Czechia", "Denmark", "Estonia", "Finland", "France", "Georgia", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Israel", "Italy", "Liechtenstein", "Monaco", "Netherlands", "Norway", "Poland", "Portugal", "Romania", "Russia", "Slovakia", "Spain", "Sweden", "Switzerland", "Ukraine", "United Kingdom"),"Europe", Country)) %>% 
  mutate(Country = ifelse(Country %in% c("China", "Hong Kong", "India", "Indonesia", "Japan", "Kazakhstan", "Lebanon", "Malaysia", "Nepal", "Oman", "Philippines", "Qatar", "Singapore", "South Korea", "Taiwan", "Thailand", "Turkey", "United Arab Emirates", "Vietnam"),"Asia", Country)) %>% 
  mutate(Country = ifelse(Country %in% c("Algeria", "Egypt", "Eswatini (Swaziland)", "Morocco", "Nigeria", "South Africa", "Tanzania" ),"Africa", Country)) %>% 
  mutate(Country = ifelse(Country %in% c("Australia", "New Zealand"),"Asia", Country)) %>% 
  mutate(across(c(Name, Country, Source, Industry),as.factor)) %>% 
  
  drop_na() 


table(df$Country)

# Sort Countries into Continents
# # North America
# "Canada", "United States"
# # South America
# "Argentina", "Barbados", "Belize", "Brazil", "Chile", "Colombia","Macau" "Guernsey", "Mexico", "Peru", "St. Kitts and Nevis", "Uruguay", "Venezuela"
# # Europe
# "Belgium", "Bulgaria", "Cyprus", "Czechia", "Denmark", "Estonia", "Finland", "France", "Georgia", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Israel", "Italy", "Liechtenstein", "Monaco", "Netherlands", "Norway", "Poland", "Portugal", "Romania", "Russia", "Slovakia", "Spain", "Sweden", "Switzerland", "Ukraine", "United Kingdom", "Austria" 
# # Asia
# "China", "Hong Kong", "India", "Indonesia", "Japan", "Kazakhstan", "Lebanon", "Malaysia", "Nepal", "Oman", "Philippines", "Qatar", "Singapore", "South Korea", "Taiwan", "Thailand", "Turkey", "United Arab Emirates", "Vietnam"
# # Africa
# "Algeria", "Egypt", "Eswatini (Swaziland)", "Morocco", "Nigeria", "South Africa", "Tanzania" 
# # Oceania
# "Australia", "New Zealand"

# Sort Industry into fewer categories

# Energy, Technology

# Entertainment, 


# Scatterplot Age and Net.Worth
p1 <- ggplot(df, aes(Age, Net.Worth)) +
  geom_point() +
  theme_minimal()+
  geom_smooth()

# barplot countries
p2 <- ggplot(df, aes(Country))+
  geom_bar()+
  theme_minimal()


table(df$Industry)




# Debugging
# table(is.na(df$Age))
# table(is.na(df$Net.Worth))
# 
# length(table(df$Country))
# 
# class(df$Age)
# class(df$Net.Worth)
# 
# 
# length(df$Net.Worth)
# length(df$Age)


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Hypothesis and Regression

H0: B_age = 0

H1: B_age != 0

Decision: Do not reject H0

```{r pressure, echo=FALSE}

model <- lm(Net.Worth ~ Age, data = df)

summary(model)

```
