---
title: "Forbes List Analysis"
author: "Josia Schramm, Bernhard Eymann, Nico Joller"
date: "`r Sys.Date()`"
output: html_document
---

## Research Question

We want to explore and analyze the Forbes List of the richest people in the world. We want to find out if the distribution of wealth is equal among the continents and the industries and if there is a correlation between age and net worth. Our hypotheses are 1: The distribution of wealth is not equal among the continents. 2: The distribution of wealth is not equal among the industries. 3: There is a correlation between age and net worth.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data, libraries

We load the tidyverse library and the data from the data_orig folder.

```{r cleaning}
library(tidyverse)
data_orig <- read.csv(here::here("data_orig", "forbes_richman.csv"))

```

## Data cleaning, transformation and summary

We clean the data by removing any non-numeric and period chars from the Net.Worth column and by transforming the Age column into a numeric column. We also sort the countries into continents and the industries into fewer categories. We drop missing values and transform the character columns into factors. And print a summary of the interesting columns.

```{r}

# Check class of cols and output tables of cols to see whats in it
# sapply(data_orig, class)
# sapply(data_orig, table)

# summary(data_orig)


# remove non integer and non "." in Net.Worth
remove_non_integer <- function(vector) {
  vector <- str_replace_all(vector, "[^0-9.]", "")
  vector <- as.numeric(vector)
  return(vector)
}

# assign original data to working df
df <- data_orig

# apply function to clean net worth
df$Net.Worth <- remove_non_integer(data_orig$Net.Worth)

# Set missing values in Age to NA
# reassign countries to continents
# reassign industry to fewer categories
# mutate chars into factors, mutate age into numeric
# drop missing values
df <- df %>% 
  mutate(Age = ifelse(Age == "N/A", NA, Age)) %>% 
  mutate(Age = as.numeric(Age)) %>%
  mutate(Country = ifelse(Country %in% c("Canada", "United States"), "North America", Country)) %>% 
  mutate(Country = ifelse(Country %in% c("Argentina", "Barbados", "Belize", "Brazil", "Chile", "Colombia","Macau", "Guernsey", "Mexico", "Peru", "St. Kitts and Nevis", "Uruguay", "Venezuela"), "South America", Country)) %>% 
  mutate(Country = ifelse(Country %in% c("Austria","Belgium", "Bulgaria", "Cyprus", "Czechia", "Denmark", "Estonia", "Finland", "France", "Georgia", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Israel", "Italy", "Liechtenstein", "Monaco", "Netherlands", "Norway", "Poland", "Portugal", "Romania", "Russia", "Slovakia", "Spain", "Sweden", "Switzerland", "Ukraine", "United Kingdom"),"Europe", Country)) %>% 
  mutate(Country = ifelse(Country %in% c("China", "Hong Kong", "India", "Indonesia", "Japan", "Kazakhstan", "Lebanon", "Malaysia", "Nepal", "Oman", "Philippines", "Qatar", "Singapore", "South Korea", "Taiwan", "Thailand", "Turkey", "United Arab Emirates", "Vietnam"),"Asia", Country)) %>% 
  mutate(Country = ifelse(Country %in% c("Algeria", "Egypt", "Eswatini (Swaziland)", "Morocco", "Nigeria", "South Africa", "Tanzania" ),"Africa", Country)) %>% 
  mutate(Country = ifelse(Country %in% c("Australia", "New Zealand"),"Asia", Country)) %>% 
  mutate(Industry = ifelse(Industry %in% c("Energy", "Technology", "Telecom", "Construction & Engineering"), "Energy & Technology", Industry)) %>% 
  mutate(Industry = ifelse(Industry %in% c("Fashion & Retail", "Food & Beverage", "Gambling & Casinos", "Media & Entertainment", "Service", "Sports"),"Entertainment & Consumption", Industry)) %>% 
  mutate(Industry = ifelse(Industry %in% c("Automotive Construction & Engineering ", "Manufacturing", "Logistics", "Metals & Mining", "Automotive"),"Industrial & Manufacturing", Industry)) %>% 
  mutate(Industry = ifelse(Industry %in% c("Real Estate", "Finance & Investments"),"Real Estate & Finance", Industry)) %>% 
  mutate(across(c(Name, Country, Source, Industry),as.factor)) %>% 
  drop_na() 


# print summary of interesting cols
summary(df[,c("Age", "Net.Worth", "Industry", "Country")])

```

## Plots & Conclusion: Hypotheses 1 & 2

We plot the distribution of richest people among the continents and the industries within which they made their fortune in two separate barplots. Conclusion: The distribution of wealth is not equal among the continents and the industries.

```{r plots, echo=FALSE}

# barplot countries make them fancier with GPT
p1 <- ggplot(df, aes(x = Country, fill = Country)) +  # Fill bars based on Country for a colorful plot
  geom_bar() +  # Default stat_count is fine here
  coord_flip() +  # Flip coordinates for horizontal bars
  scale_fill_brewer(palette = "Set2") +
  theme_minimal(base_size = 14) +  # Use a minimal theme with a larger base font size
  labs(
    title = "Where are the richest people from?",
    x = "Continent",
    y = "Count",
    fill = "Continent"  # Legend title
  ) +
  theme(legend.position = "none",  # Hide legend if not needed
        axis.text.x = element_text(angle = 45, hjust = 1),  # Adjust text angle for x-axis labels (if you decide against coord_flip)
        plot.title = element_text(size = 20, face = "bold"),  # Customize plot title
        axis.title = element_text(size = 16)) +  # Customize axis titles
  geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = 0.5), color = "white")  # Add count labels


# barplot industries, make plot fancier with GPT
p2 <- ggplot(df, aes(x = factor(1), fill = Industry)) +
  geom_bar(width = 1, stat = "count") +
  coord_polar("y", start = 0) +
  scale_fill_brewer(palette = "Set2") +  # Use a predefined color palette for clarity
  theme_void() +
  labs(title = "How did they get rich?", fill = "Industry") +  # Add a meaningful title and adjust legend title
  geom_text(aes(label = scales::percent(..count../sum(..count..))),
            position = position_stack(vjust = 0.5),
            stat = "count",
            color = "black") +  # Add percentage labels
  theme(legend.position = "bottom",  # Adjust legend position
        plot.title = element_text(hjust = 0.5, size = 16, face = "bold"))  # Center and bold the title

print(p1)
print(p2)
# We save the barplots in external files
ggsave(p1,
       filename = here::here("output", "countries.tiff"),
       device = "tiff",
       width = 6, height = 4, units = "in",
       dpi = 600,
       compress = "lzw")
ggsave(p2,
       filename = here::here("output", "industries.tiff"),
       device = "tiff",
       width = 6, height = 4, units = "in",
       dpi = 600,
       compress = "lzw")


```

## Hypothesis 3 and Regression

### Test: Plot and Regression

The hypothesis to be tested is whether age is associated with net worth.

H0: Beta_age = 0

H1: Beta_age != 0

We plot the relationship between age and net worth and perform a regression analysis.

### Interpretation

One year increase in age is (potentially) associated with a 0.028 billion increase in net worth

The p-value is 0.09, which means we can reject the null hypothesis at the alpha = 0.1 significance level, but we fail to reject the null hypothesis at alpha = 0.05 significance level

### Conclusion

It appears to be that an increase in age is somewhat correlated to an increase in net worth, but the evidence is weak, and there are many potential hidden confounders which were not adressed.

```{r model, echo=FALSE}

# Scatterplot Age and Net.Worth, make it fancier with GPT
p3 <- ggplot(df, aes(x = Age, y = Net.Worth, color = Age)) +
  geom_point(size = 3, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "blue") +
  theme_minimal(base_size = 14) +
  labs(
    title = "Do they get richer with age?",
    x = "Age",
    y = "Net Worth (in billions)"
  ) +
  theme(legend.position = "bottom")

print(p3)

ggsave(p3,
       filename = here::here("output", "age_networth.tiff"),
       device = "tiff",
       width = 6, height = 4, units = "in",
       dpi = 600,
       compress = "lzw")

model <- lm(Net.Worth ~ Age, data = df)

lmtest::coeftest(model, vcov. = sandwich::vcovHC(model, type = "HC1"))



```
